### 2020-02-13 README.Rmd

**EDA of both BigWoods & SCBI**: Note the large variation in growths for the SCBI trees over the BigWoods trees.

```{r, cache = TRUE}
growth_df <- bind_rows(
  bw_growth_df %>% select(growth) %>% mutate(site = "bw"),
  scbi_growth_df %>% select(growth) %>% mutate(site = "scbi")
)
ggplot(growth_df, aes(x = growth, y = ..density.., fill = site)) +
  geom_histogram(alpha = 0.5, position = "identity", binwidth = 0.05) +
  labs(x = "Average annual growth in dbh (cm per yr)") +
  coord_cartesian(xlim = c(-0.5, 1))
```

@@

```{r, cache = TRUE}
# Boundary polygon
square_boundary <- tibble(
  x = c(0,0,1,1),
  y = c(0,1,1,0)
) %>% 
  sf_polygon()

@@

```{r, cache = TRUE}
# Bigwoods study region boundary polygon
bw_boundary <- bigwoods_study_region %>% 
  sf_polygon()

@@

```{r, cache = TRUE}
# Bigwoods study region boundary polygon
scbi_boundary <- tibble(
  x = c(0, 0, 400, 400, 0),
  y = c(0, 640, 640, 0, 0)
) %>% 
  sf_polygon()

@@

```{r, cache = TRUE}
bw_cv_grid <- spatialBlock(
  speciesData = bw_growth_df, theRange = 100, k = 28, yOffset = 0.6
)

@@

```{r, cache = TRUE}
scbi_cv_grid <- spatialBlock(
  speciesData = scbi_growth_df, theRange = 100, k = 28, yOffset = 0.6
)

>>>>

```{r}
growth_df <- bind_rows(
  bw_growth_df %>% select(growth) %>% mutate(site = "bw"),
  scbi_growth_df %>% select(growth) %>% mutate(site = "scbi")
)
ggplot(growth_df, aes(x = growth, y = ..density.., fill = site)) +
  geom_histogram(alpha = 0.5, position = "identity", binwidth = 0.05) +
  labs(x = "Average annual growth in dbh (cm per yr)") +
  coord_cartesian(xlim = c(-0.5, 1))
```

@@

```{r}
# Boundary polygon
square_boundary <- tibble(
  x = c(0,0,1,1),
  y = c(0,1,1,0)
) %>% 
  sf_polygon()

@@

```{r}
# Bigwoods study region boundary polygon
bw_boundary <- bigwoods_study_region %>% 
  sf_polygon()

@@

```{r}
# Bigwoods study region boundary polygon
scbi_boundary <- tibble(x = c(0,400,400,0,0), y = c(0,0,640,640,0)) %>% 
  sf_polygon()

@@

```{r}
bw_cv_grid <- spatialBlock(
  speciesData = bw_growth_df, theRange = 100, k = 28, yOffset = 0.6, verbose = FALSE
)

@@

```{r}
scbi_cv_grid <- spatialBlock(
  speciesData = scbi_growth_df, theRange = 100, k = 28, yOffset = 0.6, verbose = FALSE
)
